---
title: "Visualisations"
author: "Martyna"
date: "2023-04-07"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r}
library(ggplot2)
setwd("~/dev/pregnancy_gaze")
df <- read.csv("data4analysis.csv")
```



verification that the number of trials is consistent across all tasks.
```{r}
ggplot(df, aes(x = factor(task))) + 
  geom_bar() + 
  labs(x = "Task", y = "Trial Count") +
  ggtitle("Trial Counts by Task")
```



Box plots of reaction times by task and trial type:
```{r}
ggplot(df, aes(x = factor(task), y = sacc_time, fill = factor(type))) + 
  geom_boxplot() + 
  labs(x = "Task", y = "Saccade Time (ms)", fill = "Trial Type") +
  ggtitle("Reaction Times by Task and Trial Type")


```



Density plots of peak velocity by trial type:
```{r}
c = ggplot(df, aes(x = peak_vel, color = factor(group))) + 
  geom_density() + 
  labs(x = "Peak Velocity", y = "Density", color = "Trial Type") +
  ggtitle("Peak Velocity Density by Trial Type")

c
```

Grouped bar chart of mean reaction time by type and group:
```{r}
ggplot(df, aes(x = factor(type), y = sacc_time, fill = factor(group))) + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge(), color = "black") + 
  labs(x = "Saccade Type", y = "Mean Reaction Time (ms)", fill = "Group") +
  ggtitle("Mean Reaction Time by Saccade Type and Group")

```

Grouped box plot of peak velocity by type and group:
```{r}
ggplot(df, aes(x = factor(type), y = peak_vel, fill = factor(group))) + 
  geom_boxplot(position = position_dodge()) + 
  labs(x = "Saccade Type", y = "Peak Velocity", fill = "Group") +
  ggtitle("Peak Velocity by Saccade Type and Group")

```

use the scale_y_continuous function with the limits argument to remove outliers from the box plot and focus on the main distribution of data. 
```{r}
ggplot(df, aes(x = factor(type), y = peak_vel, fill = factor(group))) + 
  geom_boxplot(outlier.shape = NA, position = position_dodge()) + 
  scale_y_continuous(limits = quantile(df$peak_vel, c(0.05, 0.95))) +
  labs(x = "Saccade Type", y = "Peak Velocity", fill = "Group") +
  ggtitle("Peak Velocity by Saccade Type and Group")
```

Grouped bar chart of error rate by type and group:
```{r}
ggplot(df, aes(x = factor(type), y = error, fill = factor(group))) + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge(), color = "black") + 
  labs(x = "Saccade Type", y = "Error Rate", fill = "Group") +
  ggtitle("Error Rate by Saccade Type and Group")

```
